Are We Reusing Outdated and Licensed Code from Stack Overflow?

### 2017-02-19 cloneoverflow-latex/cloneoverflow.tex
Added the two totals in Table 8 and in the text. Added a few FIXMEs. Fixed a total number of clone pairs manually investigated in the abstract.

\begin{abstract}
  % We studied online code clones on the popular programming Q\&A
  % website, Stack Overflow, and their issues on outdated code and
  % software licensing violations. 
  Online code clones are code fragments that are copied from software
  projects or online sources to Stack Overflow as examples in
  questions and answers.
  % They can be discovered by using code clone
  % detectors, yet they are inherently different from normal code clones
  % in software projects in several aspects. 
  Due to an absence of a checking mechanism after the code has been
  copied to Stack Overflow, online code clones may suffer from
  becoming outdated or violating the original software license.
  % Moreover, we also found that majority of online code clones do not
  % contain the license of their originals.
  We present a study incorporating several state-of-the-art tools and
  techniques to automatically extract, prioritise, and filter
  315,786,118 detected online clone pairs between 144,064 Java code
  snippets on Stack Overflow and 111 Java open source projects in the
  curated Qualitas corpus. We discovered and investigated 51,926
  non-trivial online clone candidates. Our study revealed that 64 out
  of 112 clones with strong evidence of copying from a Qualitas
  project to Stack Overflow are outdated. Furthermore, we found 357
  code snippets on Stack Overflow that violate the license of their
  original software.
  % These snippets are questionable for reuse.
  Our study is among the first to address the problem of
  outdated and license-violating code snippets on Stack Overflow.
\end{abstract}

@@

\begin{table}
\caption{FIXME Maybe merge with Table 7?}
\label{tab:snippets}
\centering
\begin{tabular}{l|rrr}
  & Pairs & Snippets & Projects \\
\hline
\textit{good} & 2,308 & 92 & 66 \\
\textit{ok'} & 11,749 & 136 & 39 \\
$S_D'$ & 17,081 & 471 & 76 \\
$N_D'$ & 88 & 77 & 29 \\
\hline
Total & 31,946 & FIXME & FIXME
\end{tabular}
\end{table}

However, using Bellon's criteria for matching clone pairs, only
0.1\textperthousand~of all pairs are agreed by two tool/configuration
combinations. As shown in FIXME, for the 2,308 \textit{good} pairs,
there are 92 Stack Overflow snippets which are associated with 66
Qualitas projects. The 11,749 \textit{ok'} pairs are clones between
136 Stack Overflow snippets and 39 Qualitas projects.  Moreover, for
the disagreed pairs, we found 17,081 clone pairs reported by $S_D'$
are clones between 471 Stack Overflow snippets and 76 Qualitas
projects and 88 $N_D'$ clone pairs are clones between 77 Stack
Overflow snippets and 29 Qualitas projects. In total we found that the
manually investigated 31,946 clones pairs are clones between FIXME
Stack Overflow snippets and FIXME Qualitas projects.

@@

\textbf{To answer RQ2, we found that a large amount of the clone pairs
  between Stack Overflow and Qualitas projects are boiler-plate code
  (28,642) or accidental clones (2,525) with no evidence that the code
  has actually been copied. Nevertheless, we found 112 pairs that had
  strong evidences to be cloned from Qualitas to Stack Overflow and
  178 pairs were found to be cloned to Stack Overflow from external
  sources outside Qualitas projects.} 
%We did not find any clone pairs in the direction from Stack Overflow to Qualitas.}

>>>>

\begin{abstract}
  % We studied online code clones on the popular programming Q\&A
  % website, Stack Overflow, and their issues on outdated code and
  % software licensing violations. 
  Online code clones are code fragments that are copied from software
  projects or online sources to Stack Overflow as examples in
  questions and answers.
  % They can be discovered by using code clone
  % detectors, yet they are inherently different from normal code clones
  % in software projects in several aspects. 
  Due to an absence of a checking mechanism after the code has been
  copied to Stack Overflow, online code clones may suffer from
  becoming outdated or violating the original software license.
  % Moreover, we also found that majority of online code clones do not
  % contain the license of their originals.
  We present a study incorporating several state-of-the-art tools and
  techniques to automatically extract, prioritise, and filter
  315,786,118 detected online clone pairs between 144,064 Java code
  snippets on Stack Overflow and 111 Java open source projects in the
  curated Qualitas corpus. We discovered and investigated 31,946
  non-trivial online clone candidates. Our study revealed that 64 out
  of 112 clones with strong evidence of copying from a Qualitas
  project to Stack Overflow are outdated. Furthermore, we found 357
  code snippets on Stack Overflow that violate the license of their
  original software.
  % These snippets are questionable for reuse.
  Our study is among the first to address the problem of
  outdated and license-violating code snippets on Stack Overflow.
\end{abstract}

@@

\begin{table}
\caption{FIXME Maybe merge with Table 7? <-- You mean Table 9?}
\label{tab:snippets}
\centering
\begin{tabular}{l|rrrr}
  & Pairs & Snippets & Projects & Avg.~C$_{\textrm{\textit{\%}}}$ \\
\hline
\textit{good} & 2,308 & 92 & 66 & \\
\textit{ok'} & 11,749 & 136 & 39 & \\
$S_D'$ & 17,081 & 471 & 76 & \\
$N_D'$ & 88 & 77 & 29 & \\
\hline
Total & 31,946 & 621 & 95 &
\end{tabular}
\end{table}

However, using Bellon's criteria for matching clone pairs, only
0.1\textperthousand~of all pairs are agreed by two tool/configuration
combinations. As shown in FIXME, for the 2,308 \textit{good} pairs,
there are 92 Stack Overflow snippets which are associated with 66
Qualitas projects. The 11,749 \textit{ok'} pairs are clones between
136 Stack Overflow snippets and 39 Qualitas projects.  Moreover, for
the disagreed pairs, we found 17,081 clone pairs reported by $S_D'$
are clones between 471 Stack Overflow snippets and 76 Qualitas
projects and 88 $N_D'$ clone pairs are clones between 77 Stack
Overflow snippets and 29 Qualitas projects. In total we found that the
manually investigated 31,946 clones pairs are clones between 621
Stack Overflow snippets and 95 Qualitas projects.

@@

\textbf{To answer RQ2, we found that a large amount of the clone pairs
  between Stack Overflow and Qualitas projects are boiler-plate code
  (28,642) or accidental clones (2,529) \FIXME{IN+AC here?} with no evidence that the code
  has actually been copied. Nevertheless, we found 112 pairs that had
  strong evidences to be cloned from Qualitas to Stack Overflow and
  178 pairs were found to be cloned to Stack Overflow from external
  sources outside Qualitas projects.} 
%We did not find any clone pairs in the direction from Stack Overflow to Qualitas.}
